A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2024-01-09 paper/fascd.tex
table 2 reproduced
replace fixme (citation) with fixme (actual rate I will now compute)

The ball problem has a known exact solution $u\in W^{2,\infty}(\Omega)$ \cite{Bueler2021,Tai2003}.  Our measured convergence rate is $\|u^\star-u^J\|_{L^2(\Omega)}=O(h^{1.98})$, as expected for $P_1$ elements.  FIXME: CITE CIARLET OR GLOWINSKI

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/drape.py
% see reproduce/table2.py
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}cccccc}
\toprule
\multirow{2}{*}{\emph{levels}} & \multirow{2}{*}{$m_J$} & \multicolumn{3}{c}{\,\emph{ball}} & \multicolumn{3}{c}{\,\emph{spiral}} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8}
   &                  & RS only & V-cycle & FMG & RS only & V-cycle & FMG \\
\midrule
% FIXME GENERATE WHOLE TABLE ON THELIO
 2 &            $145$ &   1 &  3 &  +2 &   4 &  4 &  +2 \\
 3 &            $545$ &   3 &  6 &  +3 &   6 &  5 &  +3 \\
 4 & $2.1\times 10^3$ &   6 &  7 &  +3 &   7 &  7 &  +4 \\
 5 & $8.3\times 10^3$ &  13 &  9 &  +4 &  11 &  9 &  +4 \\
 6 & $3.3\times 10^4$ &  23 & 11 &  +5 &  20 & 10 &  +5 \\
 7 & $1.3\times 10^5$ &  46 & 11 &  +4 &  35 & 11 &  +5 \\
 8 & $5.3\times 10^5$ &  90 & 12 &  +4 &  67 & 12 &  +5 \\
 9 & $2.1\times 10^6$ & \XX & 13 &  +3 & \XX & 13 &  +6 \\
10 & $8.4\times 10^6$ & \XX & 13 &  +2 & \XX & 14 &  +6 \\
11 & $3.4\times 10^7$ & \XX & 14 &  +2 & \XX & 18 &  +6 \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for Example \ref{ex:results:classical}; see text regarding cycle types and tolerances.  Runs \XX\xspace were not attempted. ``$+n$'' for FMG denotes number of V-cycles, after the FMG cycle, to satisfy \eqref{eq:stoppingcriterion}.}
\label{tab:results:classical}
\end{table}

>>>>

FIXME RATE  The ball problem has a known exact solution $u\in W^{2,\infty}(\Omega)$ \cite{Bueler2021,Tai2003}.  Our measured convergence rate is $\|u^\star-u^J\|_{H^1(\Omega)}=O(h^{1.xx})$; compare $O(h^1)$ from theory \cite[section 5.1]{Ciarlet2002}.

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/drape.py
% see reproduce/table2.py
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}cccccc}
\toprule
\multirow{2}{*}{\emph{levels}} & \multirow{2}{*}{$m_J$} & \multicolumn{3}{c}{\,\emph{ball}} & \multicolumn{3}{c}{\,\emph{spiral}} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8}
   &                  & RS only & V-cycle & FMG & RS only & V-cycle & FMG \\
\midrule
2 & 145 & 1 & 3 & +1 & 4 & 4 & +1 \\ 
3 & 545 & 3 & 6 & +2 & 6 & 5 & +2 \\ 
4 & $2.1\times 10^3$ & 6 & 7 & +2 & 7 & 7 & +3 \\ 
5 & $8.3\times 10^3$ & 13 & 9 & +3 & 11 & 9 & +3 \\ 
6 & $3.3\times 10^4$ & 23 & 11 & +4 & 20 & 10 & +4 \\ 
7 & $1.3\times 10^5$ & 46 & 11 & +3 & 35 & 11 & +4 \\ 
8 & $5.3\times 10^5$ & 90 & 12 & +3 & 67 & 12 & +4 \\ 
9 & $2.1\times 10^6$ & \XX & 13 & +2 & \XX & 13 & +5 \\ 
10 & $8.4\times 10^6$ & \XX & 13 & +1 & \XX & 14 & +5 \\ 
11 & $3.4\times 10^7$ & \XX & 14 & +1 & \XX & 18 & +5 \\ 
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for Example \ref{ex:results:classical}; see text regarding cycle types and tolerances.  Runs \XX\xspace were not attempted. ``$+n$'' for FMG denotes number of V-cycles, after the FMG cycle, to satisfy \eqref{eq:stoppingcriterion}.}
\label{tab:results:classical}
\end{table}
